A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-30 doc/paper/paper.tex
Fixup

\subsection{Benchmarks}
To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the strength of the largest input, $s > 0$ is the target separation relative to all other inputs, $\delta$ is the Kronecker delta, and $\eta_i$ is Gaussian (white) noise with standard deviation $\sigma$.
Thus, without loss of generality, the first state variable receives the largest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
It is important to note that $u$ does not only determine the size of the largest input, but also the general baseline of inputs.
Since all of the runner-ups have equal magnitude, this represents the most difficult scenario of the network's capability where all potential choices must be considered.
As $s \rightarrow 0$ the problem becomes more difficult because the utilities of the choices are closer together.
We will use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
Further, we chose noise variance increments large enough to observe the behaviour and failure as the task gets increasingly difficult.
This allows us to determine which functions are performed more robustly by each network.
In both WTA models we use 200 neurons per choice.
In the IA network this is split into 150 neurons for each layer 1 population and 50 neurons for each layer 2 population.
All remaining network parameters are summarized in Table~\ref{tbl:params}.
\begin{table}
    \caption{Summary of parameter values.}\label{tbl:params}
    \begin{tabular}{ll}
        LCA time-constant & $\tau = \SI{0.1}{\second}$ \\
        LCA recurrency parameters & $k = \beta = 1$ \\
        IA accumulation time-constant & $\tau_1 = \SI{0.1}{\second},\ \SI{0.5}{\second}$ \\
        IA feedback time-constant & $\tau_2 = \SI{0.1}{\second}$ \\
        IA threshold & $\vartheta = 0.8$ \\
        IA recurrency parameters & $\bar{\beta} = 2$ \\
        Recurrent synaptic time-constant & $\tau_{\mathrm{s}} 
        = \SI{0.1}{\second}$ \\
        Feed-forward synaptic time-constant & $\tau_{\mathrm{s}} 
        = \SI{0.005}{\second}$ \\
        Output decoding synaptic time-constant & $\tau_{\mathrm{s}} 
        = \SI{0.01}{\second}$
    \end{tabular}
\end{table}

>>>>

\subsection{Benchmarks}
To test and compare the two WTA mechanisms we provide an input of $\rho_i = u - s(1 - \delta_{1i}) + \eta_i$, where $u$ is the magnitude of the largest input, $s > 0$ is the target separation relative to all other inputs, $\delta$ is the Kronecker delta, and $\eta_i$ is Gaussian (white) noise with standard deviation $\sigma$.
Thus, without loss of generality, the first state variable receives the largest input $u$ plus noise, and all other state variables receive a noisy input that is smaller by $s$.
It is important to note that $u$ does not only determine the size of the largest input, but also the general baseline of inputs.
Since all of the runner-ups have equal magnitude, this represents the most difficult scenario of the network's capability where all potential choices must be considered.
As $s \rightarrow 0$ the problem becomes more difficult because the utilities of the choices are closer together.
We will use $u = 1$ unless indicated otherwise, and set the number of choices to $D = 10$.
Further, we chose noise variance increments large enough to observe the behaviour and failure as the task gets increasingly difficult.
This allows us to determine which functions are performed more robustly by each network.
In both WTA models we use 200 neurons per choice.
In the IA network this is split into 150 neurons for each layer 1 population and 50 neurons for each layer 2 population.
All remaining network parameters are summarized in Table~\ref{tbl:params}.
\begin{table}
    \caption{Summary of parameter values.}\label{tbl:params}
    \begin{tabular}{ll}
        LCA time-constant & $\tau = \SI{0.1}{\second}$ \\
        LCA recurrency parameters & $k = \beta = 1$ \\
        IA accumulation time-constant & $\tau_1 = \SI{0.1}{\second},\ \SI{0.5}{\second}$ \\
        IA feedback time-constant & $\tau_2 = \SI{0.1}{\second}$ \\
        IA threshold & $\vartheta = 0.8$ \\
        IA recurrency parameters & $\bar{\beta} = 2$ \\
        Recurrent synaptic time-constant & $\tau_{\mathrm{s}} 
        = \SI{0.1}{\second}$ \\
        Feed-forward synaptic time-constant & $\tau_{\mathrm{s}} 
        = \SI{0.005}{\second}$ \\
        Output decoding synaptic time-constant & $\tau_{\mathrm{s}} 
        = \SI{0.01}{\second}$
    \end{tabular}
\end{table}
